Exploratory Plots

### 2020-10-07 exploratory/2020/sub4_fitpercent.Rmd
Rename chunks to avoid conflicts

```{r sensspec}
results %>% 
  ggplot(aes(x = ref_frac, y = mcc, color = dataset)) +
  geom_jitter(size = 1, alpha = 0.3, width = 0.01) +
  stat_summary(fun = mean, geom = 'crossbar') +
  scale_color_manual(values = dataset_colors) +
  facet_grid(method ~ ref_weight) +
  labs(title='OptiFit Performance',
       x='reference fraction')
```

```{r runtime}
results %>% ggplot(aes(x=num_ref_seqs, y=s, color=dataset)) +
  geom_point(alpha = 0.3) +
  facet_grid(method ~ ref_weight) +
  scale_color_manual(values = dataset_colors) +
  scale_x_continuous(breaks = seq(0, 200000, 50000),
                     labels = c('0', '50k', '100k', '150k', '200k')) +
  labs(title = 'Runtime over reference size',
       x = '# sequences in reference',
       y = 'seconds')
results %>% 
  ggplot(aes(x=numotus, y=s, color=dataset)) +
  geom_point(alpha = 0.5) +
  facet_grid(method ~ ref_weight) +
  scale_color_manual(values = dataset_colors) +
  #scale_x_continuous(breaks = seq(0, 40000, 10000),
  #                   labels = c('0', '10k', '20k', '30k', '40k')) +
  labs(title = 'Runtime over number of OTUs',
       x = '# OTUs',
       y = 'seconds')
```

```{r fraction_mapped}
results %>% 
  group_by(dataset, ref_weight, ref_frac) %>% 
  ggplot(aes(x=ref_frac, y=fraction_mapped, color=dataset)) +
  geom_jitter(alpha = 0.5, width = 0.01, size=1) +
  scale_color_manual(values = dataset_colors) +
  facet_wrap("ref_weight") +
  ylim(0, 1) +
  labs(title="Sequences mapped during closed-reference OptiFit",
       x='reference fraction',
       y='fraction mapped')
```

>>>>

```{r sensspec_fitpercent}
results %>% 
  ggplot(aes(x = ref_frac, y = mcc, color = dataset)) +
  geom_jitter(size = 1, alpha = 0.3, width = 0.01) +
  stat_summary(fun = mean, geom = 'crossbar') +
  scale_color_manual(values = dataset_colors) +
  facet_grid(method ~ ref_weight) +
  labs(title='OptiFit Performance',
       x='reference fraction')
```

```{r runtime_fitpercent}
results %>% ggplot(aes(x=num_ref_seqs, y=s, color=dataset)) +
  geom_point(alpha = 0.3) +
  facet_grid(method ~ ref_weight) +
  scale_color_manual(values = dataset_colors) +
  scale_x_continuous(breaks = seq(0, 200000, 50000),
                     labels = c('0', '50k', '100k', '150k', '200k')) +
  labs(title = 'Runtime over reference size',
       x = '# sequences in reference',
       y = 'seconds')
results %>% 
  ggplot(aes(x=numotus, y=s, color=dataset)) +
  geom_point(alpha = 0.5) +
  facet_grid(method ~ ref_weight) +
  scale_color_manual(values = dataset_colors) +
  #scale_x_continuous(breaks = seq(0, 40000, 10000),
  #                   labels = c('0', '10k', '20k', '30k', '40k')) +
  labs(title = 'Runtime over number of OTUs',
       x = '# OTUs',
       y = 'seconds')
```

```{r fraction_mapped_fitpercent}
results %>% 
  group_by(dataset, ref_weight, ref_frac) %>% 
  ggplot(aes(x=ref_frac, y=fraction_mapped, color=dataset)) +
  geom_jitter(alpha = 0.5, width = 0.01, size=1) +
  scale_color_manual(values = dataset_colors) +
  facet_wrap("ref_weight") +
  ylim(0, 1) +
  labs(title="Sequences mapped during closed-reference OptiFit",
       x='reference fraction',
       y='fraction mapped')
```
